Wolbachia and Two Other Microbes Nobody Cares About That Changed The World Kinda

### 2015-12-16 paper.tex
Last section header added
added a bit about Wallace

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[width=.4\textwidth]{images/cordyceps_ant.jpg}
    \caption{The spore bearing fruiting body of \textit{Ophiocordyceps unilateralis} growing out of the back of the head of an ant whose mandibles are tightly gripping a twig. }
    \label{fig:cordyceps_ant}
\end{figure}

\textit{Ophiocordyceps unilateralis} was first discovered by the British naturalist Alfred Russel Wallace who, probably not coincidently, is best known for independently conceiving the theory of evolution through natural selection.
